City traffic, IoT and Blockchain technologies

### 2020-11-02 thesis/report2.tex
Continued on the report 2.

    \paragraph{Security} Security in Ethereum is a complex process. If an account, being a user's account or a contract account, has successfully secured the private signing key, it is assured that no one can simulate it and no one can execute transactions on its behalf. Known breaches have always occured in the same way: private keys have been leaked and malicious actors were able to execute transactions with them.

@@

@@

>>>>

    Security in Ethereum is a complex process with many faces. It drives the entire reason of why ht nature of Ethereum is so different than a centralized solutin. If an account, being a user's account or a contract account, has successfully secured the private signing key, it is assured that no one can simulate it and no one can execute transactions on its behalf. Known breaches have always occured in the same way: private keys have been leaked and malicious actors were able to execute transactions with them. But for this mechanism to work the rest of the blockchain infrastructure is complex enough to not fit into this paragraph. It is worth, though, to be noted few aspects. The extensive use of private/public key pair is the first one. Second, the Keccak256 hashing algorithm are used to generate proof of works. Those proof of works will be discussed widely in the section \ref{sec:PoWandPoS} but for this section it is important to mention them as they have an immense value in providing the security of mining a transaction. All miners are racing up to find a solution using the Keccak256 hashing algorithm and all of them are obliged to so because of consensus rules. Any of them which would try to trick this step will lose money. Thus the security of mining transactions and making sure the transaction is made by the true owner and the money are received by the true intended recipient are baked into the rules used for finding the proof of work and reaching consensus among the enire blockchain.

@@

    Data assurance and resilience are two themes within the big concept of Blockchain security. In \cite{TowardsdatAassuranceAndResilience} the authors are describing a mechanism for drones that achieves few objectives like trusted data origin (allows to know for sure which drone send a part of data), instant and permanent data integrity (data cannot be tampered with on during its entire travel from drones to the blockchain or to the database). The mechanism involved here is generaaly known as Public Key Infrastructure (PKI). PKI encompasses all the operations, storage, key generation, keys transmission, key rotation, etc. needed for ensuring a crucial aspect for the entities which are communicating in a system: a message can be verified that it was sent by the entity which claims it sent it while the message cannot be tampered with by a man-in-the-middle attack.

@@

    IOTA is a distributed ledger technology, but not a blockchain, that allows devices in a IOTA network to transact in micropayments and to send each other immutable data. One crucial difference between IOTA and a blockchain is the how the transactions are linked together. In blockchain-type technologies, as the name implies, a transaction references only the one behind it and is referenced only by the one which comes next. In IOTA, being a distributed ledger technology (DLT), a transaction can reference multiple transactions which were made earlier and can be referenced by multiple transactions which comes after it. This is known as direct acyclic graph (DAG). Another crucial difference between a blockchain and IOTA DLT is the consensus mechanism. In the blockchain the consensus is made through the proof of work by the miners. In IOTA there are no miners and there is no proof of work. Instead there is an entity called The Coordinator or more recently Coordicide. Their aim is to validate transactions without requiring a proof of work mechanism. The main reason for this is to give the ability of participating to many other types of devices which otherwise do not have the power of doing proof of work tasks.
